\documentclass[12pt]{article}

\begin{document}

\begin{thebibliography}{99}

\bibitem{1} 
Bauman, Eric.
\textit{Game-Based Teaching and Simulation in Nursing and Health Care}. 
New York 2014.

\bibitem{2} 
Benito, Jorge; Gonzalez, Enara.
\textit{Enterprise Augmented Reality Projects: Build real-world, large-scale AR solutions for various industries}. 
Boston 2019.

\bibitem{3} 
Bourdot, Patrick; Interrante, Victoria; Nedel, Luciana.
\textit{Virtual Reality and Augmented Reality}. 
Cham 2019.

\bibitem{4} 
Bourdot, Patrick; Paolis, Lucio.
\textit{Augmented Reality, Virtual Reality, and Computer Graphics}. 
Santa Maria al Bagno 2019.

\bibitem{5} 
Dieck, Claudia; Jung, Timothy.
\textit{Augmented Reality and Virtual Reality: Empowering Human, Place and Business}. 
Cham 2018.

\bibitem{6} 
Hollerer, Tobias; Schmalstieg, Dieter.
\textit{Augmented Reality: Principles and Practice}. 
Boston 2016.

\bibitem{7} 
Macaudaand Anita; Panciroli, Chiara; Russo, Veronica.
\textit{Educating about Art by Augmented Reality: New Didactic Mediation Perspectives at School and in Museums}. 
Bologna 2018.

\bibitem{8} 
Malespina, Elissa.
\textit{Augmented Reality in Education: Bringing Interactivity to Libraries and Classrooms}. 
London 2018.

\bibitem{9} 
Marisol, Hernandez; Ruiz, Gerardo.
\textit{Augmented Reality for Enhanced Learning Environments}. 
Mexico 2018.

\bibitem{10} 
Mohamudally, Nawaz.
\textit{State of the Art Virtual Reality and Augmented Reality Knowhow}. 
London 2018.

\bibitem{11} 
Papagiannis, Helen.
\textit{Augmented Human: How Technology Is Shaping the New Reality}. 
New York, Tel Aviv 2017.

\bibitem{12} 
Prodromou, Theodosia.
\textit{Augmented Reality in Educational Settings}. 
Boston 2020.

\bibitem{13} 
Shumaker, Randall.
\textit{Virtual, Augmented and Mixed Reality: Systems and Applications}. 
London, New York 2014.

\bibitem{14} 
Simao, Emilia; Soares, Celia.
\textit{Trends, Experiences, and Perspectives in Immersive Multimedia and Augmented}. 
Hershey 2019.

\bibitem{15} 
Yurt, Meltem.
\textit{Storytelling with Augmented Reality}. 
Baden-Baden 2019.

\end{thebibliography}

\end{document}