\documentclass{article}
\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\renewcommand{\thesection}{\Roman{section}} 

\title{Wybrane prace promotora: dr. Grzegorza Sokala}
\author{Paweł Strzeszkowski}
\date{\today}

\begin{document}

\maketitle

\section{Najczęściej cytowane}

\begin{enumerate}
    \item Gluzman, S., Mityushev, V., Nawalaniec, W., Sokal, G. (2016). Random composite: stirred or shaken. Archives of Mechanics, 68(3), 229-241.
    \item Sładek, J., Sokal, G., Ostrowska, K., Kmita, A. (2007). Wzorcowanie współrzędnościowych ramion pomiarowych (WRP). Acta mechanica et automatica, 1(2), 53-58.
    \item Sokal, G. (2005). Metoda podwyższenia dokładności pomiarów współrzędnościowych dokonywanych przez roboty przemysłowe.
    \item Sładek, J., Kupiec, R., Sokal, G., Krawczyk, M. (2010). Laser tracker system adaptation for the analysis of selected functional characteristics of industrial robots.
    \item Tomczyk, K., Piekarczyk, M., Sokal, G. (2019). Radial Basis Functions Intended to Determine the Upper Bound of Absolute Dynamic Error at the Output of Voltage-Mode Accelerometers. Sensors, 19(19), 4154.
\end{enumerate}

\section{Najbardziej aktualne}

\begin{enumerate}
    \item Tomczyk, K., Piekarczyk, M., Sokal, G. (2019). Radial Basis Functions Intended to Determine the Upper Bound of Absolute Dynamic Error at the Output of Voltage-Mode Accelerometers. Sensors, 19(19), 4154.
    \item Gluzman, S., Mityushev, V., Nawalaniec, W., Sokal, G. (2016). Random composite: stirred or shaken. Archives of Mechanics, 68(3), 229-241.
    \item Sokal G., Majchrzyk M., (2013). Comparing the performance of virtual environments operating systems Linux and Windows in modeling RAID.
    \item Sładek, J., Sokal G. (2010). Advances in coordinate, 138-147
    \item Sładek, J. Sokal, G., Ostrowska, K. (2007). Acta Mechanica et Automatica, 56-58
\end{enumerate}

\end{document}

